Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
small change fig 2

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   ([xshift=10.5cm]aux2) edge node[align=center] {Increase $k$} (aux1);

>>>>

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   ([xshift=10.5cm]aux2) edge node[align=center] {Increase Completeness Threshold} (aux1);
